Irreducible Components and Dimension of the Springer Fiber of a Hook-Type Slodowy Slice

### 2024-09-02 paper.tex
Revert "stuff to revert"
This reverts commit dcfef4b5c5a0744446c6976c4a63d06dc1158fdb.

\section{Strategy for Finding Components of \texorpdfstring{\(\mathcal{P}_{J(\lambda)}\)}{P\_\{J(\textbackslash lambda)\}}}\label{p_comp_strat}
\par Let \(X = J(\lambda) \in \gl_m\), where \(\lambda = (\lambda_1, ..., \lambda_\ell)\).
In this section we write \(\mathcal{P} := \mathcal{P}_X\) and \(A_{a, b} := A_{X, a, b}\).
Let \((e_{ij})_{1 \leq i \leq k, 1 \leq j \leq \lambda_i}\) be the standard basis for \(\mathbb{C}^m\).
Let \((f_j)_{1 \leq j \leq k}\) be the standard basis for \(\mathbb{C}^n\).
We index the bases such that \(Xe_{ij} = e_{i,j - 1}\), and \(J_n f_j = f_{j - 1}\).
\par For \(1 \leq w \leq \ell\) and \(0 \leq r \leq \lambda_w - 1\), define \(\mathcal{P}_{w,r}\) as the set of \((A_{a,b}, V_\bullet) \in \mathcal{P}\) such that there exist \(P \in \GL_m\) and \(b' \in \mathbb{C}^m\) such that \((P^{-1}, I_n) A_{a, b} (P, I_n) = A_{e_{w,r + 1}, b'}\).
Also, for \(1 \leq w \leq \ell\), define \(\mathcal{P}_{w,\lambda_w}\) as the set of \((A_{a,b}, V_\bullet) \in \mathcal{P}\) such that there exist \(P \in \GL_m\) and \(b' \in \mathbb{C}^m\) such that \((P^{-1}, I_n)A_{a,b}(P,I_n) = A_{0,b'}\).
\par The point of the definition above is that \((A_{a,b}, V_\bullet) \in \mathcal{P}_{wr}\) if and only if we can change basis of \(\mathbb{C}^m\) to get from \(A_{a,b}\) to some \(A_{a',b'}\) such that (1) \(a'_{ij} = 0\) for \(i \neq w\), and (2) \(a_{wj}' = 0\) for all but (at most) one \(j\), and (3) \(r\) is the biggest number s.t. \(a_{w1}' = a_{w2}' = \cdots = a_{wr}' = 0\).

\begin{lemma}\label{pwr_union}
    \(\mathcal{P} = \bigcup_{1 \leq w \leq k, 0 \leq r \leq \lambda_{w}} \mathcal{P}_{wr}\).
\end{lemma}
\begin{proof}
    For any \(a \in \mathbb{C}^m\), define the linear map \(\phi_a : \mathbb{C}^{m + n} \to \mathbb{C}\) by \(e_{ij} \mapsto a_{ij}\) and \(f_j \mapsto 0\).
    Note that \(A_{a,b}\) is the unique linear map \(\mathbb{C}^{m + n} \to \mathbb{C}^{m + n}\) that sends \(e_{ij}\) to \(e_{i,j-1} + \phi_a(e_{ij}) f_n\), sends \(f_{i + 1}\) to \(f_i\), and sends \(f_1\) to \((b, 0)\).
    \par Let \((A_{a, b}, V_\bullet) \in \mathcal{P}\).
    Since \(X\) is nilpotent, \cref{normalization} says that there is a change of basis \(P : \mathbb{C}^m \to \mathbb{C}^m\) such that the vectors \(Pe_{ij}\) form a Jordan basis for \(X\), and for all but one pair \((i, j)\) we have \(\phi_a(Pe_{ij}) = 0\).
    \par Since \((Pe_{ij})_{ij}\) is a Jordan basis, we have \((P^{-1}, I_n) A_{a,b}(P, I_n) = A_{a',b'}\) for some \(a',b' \in \mathbb{C}^m\).
    All that is left is to show that \(a'_{ij} = 0\) for all but one pair \((i,j)\).
    Indeed, this results from the fact that \(\phi_{a'}(e_{ij}) = \phi_a(Pe_{ij}) = 0\) for all but one pair \((i,j)\).
\end{proof}
\begin{lemma}
    \(\mathcal{P}_{w_1r_1} = \mathcal{P}_{w_2r_2}\) exactly when either \(\lambda_{w_1} - r_1 = \lambda_{w_2} - r_2 = 0\), or \((\lambda_{w_1}, r_1) = (\lambda_{w_2}, r_2)\).
\end{lemma}
\begin{proof}
    If \(r_1 = \lambda_{w1}\) and \(r_2 = \lambda_{w_2}\), then by definition, \(\mathcal{P}_{wr_1} = \mathcal{P}_{wr_2}\).
    And if \((\lambda_{w_1}, r_1) = (\lambda_{w_2}, r_2)\), then any matrix of the form \(A_{e_{w_1r_1}b'}\) can be transformed to a matrix of the form \(A_{e_{w_2r_2}b'}\) by making the change of basis that swaps \(e_{w_1j}\) with \(e_{w_2j}\).
    \par Conversely, suppose \(\mathcal{P}_{w_1r_1} = \mathcal{P}_{w_2r_2}\).
    Let \(k \geq 0\) be minimal such that there exists \(v \in \mathbb{C}^m\) with \(A_{e_{w_1r_1},0} f_1 \neq 0\).
    Obviously \(k = r_1\).
    Since (by hypothesis) \(A_{e_{w_1r_1},0}\) and \(A_{e_{w_2r_2},0}\) differ only by a change of basis of \(\mathbb{C}^m\), the same reasoning shows that \(k = r_2\).
    Hence \(r_1 = r_2\).
    Now, if \(r_1 = 0\), we are done.
    \par Otherwise, \(r_1 > 0\).
    Let \(k' \geq 0\) be maximal such that \(\exists v \in \mathbb{C}^m. \; A_{e_{w_1r_1},0}^{k'} v = A_{e_{w_1r_1},0} f_1\).
    Obviously \(k' = \lambda_{w_1} - r_1\).
    Clearly \(k'\) is independent of \(\mathbb{C}^m\)-basis, so \(\lambda_{w_1} - r_1 = k' = \lambda_{w_2} - r_2\).
\end{proof}

>>>>

\section{Strategy for Finding Components of \texorpdfstring{\(\mathcal{P}_{J(\lambda)}\)}{P\_\{J(\textbackslash lambda)\}}}\label{p_comp_strat}
\par Let \(X = J(\lambda) \in \gl_m\), where \(\lambda = (\lambda_1, ..., \lambda_\ell)\).
In this section we write \(\mathcal{P} := \mathcal{P}_X\) and \(A_{a, b} := A_{X, a, b}\).
Let \((e_{ij})_{1 \leq i \leq k, 1 \leq j \leq \lambda_i}\) be the standard basis for \(\mathbb{C}^m\).
Let \((f_j)_{1 \leq j \leq k}\) be the standard basis for \(\mathbb{C}^n\).
We index the bases such that \(Xe_{ij} = e_{i,j - 1}\), and \(J_n f_j = f_{j - 1}\).
\par For \(1 \leq w \leq \ell\) and \(0 \leq r \leq \lambda_w\) (note that we allow \(r = 0\); recall \(e_{i0} = 0\)), define \(\mathcal{P}_{w,r}\) as the set of \((A_{a,b}, V_\bullet) \in \mathcal{P}\) such that there exist \(P \in \GL_m\) and \(b' \in \mathbb{C}^n\) such that \((P^{-1}, I_n) A_{a, b} (P, I_n) = A_{e_{wr}, b'}\).

\begin{lemma}\label{pwr_union}
    \(\mathcal{P} = \bigcup_{1 \leq w \leq k, 0 \leq r \leq \lambda_{w}} \mathcal{P}_{wr}\).
\end{lemma}
\begin{proof}
    For any \(a \in \mathbb{C}^m\), define the linear map \(\phi_a : \mathbb{C}^{m + n} \to \mathbb{C}\) by \(e_{ij} \mapsto a_{ij}\) and \(f_j \mapsto 0\).
    Note that \(A_{a,b}\) is the unique linear map \(\mathbb{C}^{m + n} \to \mathbb{C}^{m + n}\) that sends \(e_{ij}\) to \(e_{i,j-1} + \phi_a(e_{ij}) f_n\), sends \(f_{i + 1}\) to \(f_i\), and sends \(f_1\) to \((b, 0)\).
    \par Let \((A_{a, b}, V_\bullet) \in \mathcal{P}\).
    Since \(X\) is nilpotent, \cref{normalization} says that there is a change of basis \(P : \mathbb{C}^m \to \mathbb{C}^m\) such that the vectors \(Pe_{ij}\) form a Jordan basis for \(X\), and for all but one pair \((i, j)\) we have \(\phi_a(Pe_{ij}) = 0\).
    \par Since \((Pe_{ij})_{ij}\) is a Jordan basis, we have \((P^{-1}, I_n) A_{a,b}(P, I_n)\) for some \(a',b' \in \mathbb{C}^m\).
    All that is left is to show that \(a'\) is of the form \(e_{wr}\) for some \(w\) and \(r\).
    Indeed, this results from the fact that \(\phi_{a'}(e_{ij}) = \phi_a(Pe_{ij}) = 0\) for all but one pair \((i,j)\).
\end{proof}
\begin{lemma}
    \(\mathcal{P}_{w_1r_1} = \mathcal{P}_{w_2r_2}\) exactly when either \(r_1 = r_2 = 0\), or \((\lambda_{w_1}, r_1) = (\lambda_{w_2}, r_2)\).
\end{lemma}
\begin{proof}
    If \(r_1 = r_2 = 0\), we have \(e_{wr_1} = e_{wr_2} = 0\), so by definition, \(\mathcal{P}_{wr_1} = \mathcal{P}_{wr_2}\).
    And if \((\lambda_{w_1}, r_1) = (\lambda_{w_2}, r_2)\), then any matrix of the form \(A_{e_{w_1r_1}b'}\) can be transformed to a matrix of the form \(A_{e_{w_2r_2}b'}\) by making the change of basis that swaps \(e_{w_1j}\) with \(e_{w_2j}\).
    \par Conversely, suppose \(\mathcal{P}_{w_1r_1} = \mathcal{P}_{w_2r_2}\).
    Let \(k \geq 0\) be minimal so that \(A_{e_{w_1r_1},0} f_1 \neq 0\).
    Obviously \(k = r_1\).
    Since (by hypothesis) \(A_{e_{w_1r_1},0}\) and \(A_{e_{w_2r_2},0}\) differ only by a change of basis of \(\mathbb{C}^m\), the same reasoning shows that \(k = r_2\).
    Hence \(r_1 = r_2\).
    Now, if \(r_1 = 0\), we are done.
    \par Otherwise, \(r_1 > 0\).
    Let \(k' \geq 0\) be maximal such that \(\exists v \in \mathbb{C}^m. \; A_{e_{w_1r_1},0}^{k'} v = A_{e_{w_1r_1},0} f_1\).
    Obviously \(k' = \lambda_{w_1} - r_1\).
    Clearly \(k'\) is independent of \(\mathbb{C}^m\)-basis, so \(\lambda_{w_1} - r_1 = k' = \lambda_{w_2} - r_2\).
\end{proof}
